### 2021-04-22 Chapter-5/Chapter-5.tex
Update Chapter-5.tex

Side-channel attacks can be seen as a process that refers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}. As an attacker, he can observe the memory address of the victim program. He wants to infer the original secret ($k$) based on the observation. We also assume the attacker knows the known message $m \in M$. In the rest of paper, we use $\beta(K) \rightarrow O$ to denote a victim program with side-channel vulnerabilities.

>>>>

Side-channel attacks can be seen as a process that infers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}. As an attacker, he can observe the memory address of the victim program. He wants to infer the original secret ($k$) based on the observation. We also assume the attacker knows the known message $m \in M$. In the rest of paper, we use $\beta(K) \rightarrow O$ to denote a victim program with side-channel vulnerabilities.
